---
title: "Homework10"
author: "Zhuofei Xie"
date: "11/22/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(broom)
library(dplyr)
library(tidyr)
library(modelr)
```

```{r}
mod <- lm(mpg ~ ., data = mtcars)
prediction <- augment(mod, mtcars) %>% 
  select(.rownames, mpg, .fitted) 
head(prediction) 
```

**1. Compute the sum of squared errors from the fitted regression model. **
```{r}
SSE <- 0
terminal <- nrow(prediction)
for (i in 1:terminal) {
  SSE = SSE + (prediction[i,2] - prediction[i,3])^2
}
SSE
```

**2. With suitable assumptions on the population, which coefficients are significantly different from zero? [Hint: the answer is either all or nothing.]**
```{r}
summary(mod)
```
All coefficients are siginificantly different from zero. 


```{r}
quantile(mtcars$mpg)
mtcars %>% 
  group_by(cyl) %>% 
  summarise(
    q = list(quantile(mpg))) %>% 
  unnest()
```

```{r}
probs <- c(0.01, 0.25, 0.5, 0.75, 0.99)
mtcars %>% 
  group_by(cyl) %>% 
  summarise(
    p = list(probs), 
    q = list(quantile(mpg,probs))
  ) %>% 
  unnest()
```

```{r}
set.seed(1) 
folds <- crossv_kfold(mtcars, k = 5)
folds
```

**3. What are the row numbers in the first partition of the “training” data? Notice that the first train object references all rows except 5, 9, 17, 20, 27, 28, 29.**
```{r}
library(modelr)
set.seed(1)
folds <- crossv_kfold(mtcars, k = 5)
folds
folds$train[[1]]
folds$test[[1]]
```
The row numbers in the first partition of the "training" data is 1,2,3,5,6,8,9,10,11,13,14,15,16,17,18,19,20,22,23,24,25,26,28,30,32


**4. Confirm that the SSE from cross validation is much larger than the SSE from Exercise 1.**
```{r}
library(purrr)
folds <- folds %>% mutate(model = map(train, ~ lm(mpg ~ ., data = .)))
folds %>% mutate(predicted = map2(model, test, ~ augment(.x, newdata = .y)))

library(tidyr)
cv.pred <- folds %>% mutate(predicted = map2(model, test, ~ augment(.x, newdata = .y))) %>% unnest(predicted)
head(cv.pred)

cv.pred %>% summarise(SSE =  sum((mpg - .fitted)^2))
```
The result we get from exercise 1 is around 147. Comparing with around 685 fot this question. 





































