---
title: "Homework8"
author: "Zhuofei Xie"
date: "11/1/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mdsr)
library(modelr)
library(dplyr)
```


```{r eval=FALSE, echo=FALSE}
grid <- RailTrail %>% 
  data_grid(hightemp) 
grid 

grid <- grid %>% 
  add_predictions(mod1) 
grid
```


```{r eval=FALSE,  echo=FALSE}
ggplot(data = RailTrail, aes(x = hightemp, y = volume)) + geom_point() + geom_smooth(method = lm, se = FALSE) + geom_line(aes(y = pred), data = grid, colour = "red", size = 1)

mod1 <- lm(volume ~ hightemp, data = RailTrail)

mod2 <- loess(volume ~ hightemp, data = RailTrail)
```

```{r eval=FALSE, echo=FALSE}
RailTrail_r <- RailTrail %>% 
  add_residuals(mod1) %>% 
  dplyr::select(hightemp,volume,resid)
RailTrail_r

ggplot(data = RailTrail_r, aes(x = hightemp, y = resid)) + geom_ref_line(h = 0) + geom_point()
```





**1. Use add_predictions() to add predictions to your original dataset.**
```{r}
mod1 <- lm(volume ~ hightemp, data = RailTrail)

mod2 <- loess(volume ~ hightemp, data = RailTrail)

RailTrail_hightemp <- RailTrail %>% 
  select(hightemp)

RailTrail_hightemp_lm <- RailTrail_hightemp %>% 
  add_predictions(mod1) 
head(RailTrail_hightemp_lm)

```

**2. The power of data_grid() is in generating all combinations of potential data points. Modify the following code to create a data grid for variables hightemp, weekday, cloudcover, and precip. Check that the resulting data grid has more data points than the original dataset.**
```{r}
grid2 <- RailTrail %>% 
  data_grid(hightemp,weekday,cloudcover,precip) 
grid2
head(grid2)
```

The original dataframe only has 90 rows. However, after we use data_grid(hightemp, weekday, couldover, orecip), we got 95040 rows data. We have more data points than the original dataset. 


**3. Use add_predictions() and add_residuals() to visualize the nonparametric regression curve and the residuals. [Hint: The advantage of this approach is that it will work with any model in R, from the simplest to the most complex.]**
```{r}
RailTrail_hightemp_losses <- RailTrail_hightemp %>% 
  add_predictions(mod2)
head(RailTrail_hightemp_losses)

ggplot(RailTrail, aes(hightemp)) + geom_point(aes(y = volume)) + geom_line(aes(y = pred), RailTrail_hightemp_losses, size = 1, color = "blue")
```
```{r}
RailTrail_r_losses <- RailTrail %>% 
  add_residuals(mod2) %>% 
  dplyr::select(hightemp,volume, resid)
head(RailTrail_r_losses)

ggplot(RailTrail_r_losses, aes(hightemp,resid)) + geom_ref_line(h = 0) + geom_point()
```




